\documentclass[margin,line]{res}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}


\usepackage{fontawesome5}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0} 

\usepackage{array}
\newcolumntype{L}{>{\arraybackslash}p{4.5in}}


\begin{document}

\name{Michael Boerman \vspace*{.1in}}

\begin{resume}
\section{\sc Contact}
\vspace{.05in}

\faEnvelope  {\ttfamily \, hireme@michaelboerman.com} \\
\faLinkedinIn  \href{https://wwwlinkedin.com/in/michael-boerman}{\ttfamily \, \, linkedin.com/in/michael-boerman}\\

\section{\sc Portfolio}
\faIcon{video} \href{https://www.youtube.com/channel/UCxFMrMb6PrS7SOrQi-BfMUw/videos?view=0&sort=p&flow=grid}{ Explained by Michael YouTube channel}\\
\faChartLine \href{https://github.com/michaelboerman/lockdown_severity_index#readme}{\, Covid Lockdown Severity Index}\\
\faMediumM \href{https://michaelboerman.com/}{\ttfamily  \, michaelboerman.com}\\


\section{\sc Education}
{\bf Harvard} Extension School, Cambridge, MA, USA\\
2021 - present\\
Graduate Certificate in Programming\\

{\bf Georgia Tech}, Atlanta, GA, USA\\
2019 - 2020\\
GPA: 4.0/4.0\\
M.S. in Economics, concentration in econometrics\\

{\bf University of Alabama in Huntsville}, Huntsville, AL, USA\\
2015 - 2019\\
GPA: 4.0/4.0\\
B.S. in Industrial \& Systems Engineering; Minor in Astrophysics\\
Senior Theses: \\
\hspace{5mm}{\it -- Systems Engineering:} \href{https://tinyurl.com/ISEEM-SD}{NASA Mars Lander propulsion system}\\
\hspace{5mm}{\it -- Economic Decision Analysis:} \href{http://tinyurl.com/BoermanCareerChoice
}{Career Comparison Tool}

\section{\sc Job History}
{\bf Federal Reserve Board of Governors}\\
May 2020 - {\it Present}\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:  & Research \& Statistics}\\
    {Section:   & Current-Macroeconomic Conditions}\\
    {Job Title: & Research Assistant}\\
    {Skills Developed: & R, Shiny, linux, shell scripts, version control (git), \LaTeX, research process, agile}\\
    {Responsibilities: & Re-factoring code (R and MATLAB), writing new code for models, writing new code for plots and tables, collecting and cleaning data for research projects}\\
    {Projects Worked:  & Macroeconomic now-casting models for use in monetary policy}\\
    {Links to Work:    & -\href{https://michaelboerman.medium.com/predicting-the-present-a56ff704af0b}{Predicting the Present}\\&  -\href{https://github.com/michaelboerman/lockdown_severity_index#readme}{Covid Lockdown Severity Index}}\\
\end{tabular}\\


\section{\sc Intern \& Part-time Experience}
{\bf Boeing}\\
May 2018 - August 2018\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & Space, Defense, and Security}\\
    {Section:          & Systems Engineering, Integration, and Testing}\\
    {Job Title:        & Systems Engineering Intern}\\
    {Skills Developed: & IBM Rational DOORS, ProE CAD, project management}\\
    {Projects Worked:  & NASA Space Launch System - EUS and ICPS}\\
    {Responsibilities: & Created text databases of requirements for multiple sub-contractors. Traced hydrogen fuel lines throughout rocket to verify connections.}\\
\end{tabular}\\


May 2017 - August 2017\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & Commercial Aircraft}\\
    {Section:          & Interiors: Monuments & Galleys}\\
    {Job Title:        & Supply Chain Analyst Intern}\\
    {Skills Developed: & MS Visio, supply chain management}\\
    {Projects Worked:  & 747, 787}\\
    {Responsibilities: & Performed supplier qualifications and assessments. Reduced installation damage.}\\
\end{tabular}\\

{\bf Fulfyld}\\
August 2018- December 2018\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & Warehousing}\\
    {Job Title:        & Process Improvement Engineer Intern}\\
    {Skills Developed: & 5S, six-sigma, process improvement, minitab}\\
    {Responsibilities: & Workplace organization, created and maintained work instructions, facility layout, cycle time analysis, and lean workflow. Designed and implemented ergonomic user workstations and using systematic layout planning for product locations in a new warehouse.}\\
\end{tabular}\\


{\bf General Electric}\\
May 2016- August 2016\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & Appliances}\\
    {Section:          & Supplier Quality Engineering}\\
    {Job Title:        & Quality Engineer Co-Op}\\
    {Skills Developed: & 5S, process improvement, Excel}\\
    {Responsibilities: & Tested and analyzed malfunctioning electrical components. Detected trends from this data and subsequently worked with suppliers to correct these issues. Facilitated supplier transitions and ensured quality during these transitions. Implemented new manufacturing process that reduced manufacturing cost while improving quality.}\\
\end{tabular}\\

{\bf The University of Alabama in Huntsville}\\
August 2016 - July 2019\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & Student Success Center}\\
    {Job Title:        & Academic Tutor}\\
    {Responsibilities: & Tutored over 100 unique students in over 400 sessions in the following subjects:  Calculus 1, 2, 3, Linear Algebra, Differential Equations, Statics, Thermodynamics, Mechanics of Materials, Probability/Statistics for Engineers I \& II; Engineering Economy, Operations Research, Intro to Industrial and Systems Engineering, Statistical Quality Control, Systems Analysis and Management, Physics 1\&2, Astronomy 1\&2, Astrophysics I.}\\
\end{tabular}\\

August 2016 - May 2018\\
\vspace{-.65cm}

\begin{tabular}{lL}
    {Division:         & College of Engineering}\\
    {Job Title:        & Engineering Ambassador}\\
    {Responsibilities: & Represented the College of Engineering of UAH in recruiting/outreach events and provided support for incoming engineering students. Created curriculum, planned, coordinated, and led STEM activities and competitions for students at local middle and high schools.}\\
\end{tabular}\\




\vspace{.75cm}
\section{\sc Scholarships, Awards, and Grants} 

{\bf School of Economics Fellowship}, Georgia Tech, 2019 (\$1,500)
\vspace*{-3.5mm}

{\bf UAH Alumni Association Scholarship}, Univ Alabama Huntsville, 2019 (\$4,000)
\vspace*{-3.5mm}

{\bf HASBAT Scholarship}, Huntsville Assoc. of Businesses of Advanced Technology, 2017 (\$1,500)
\vspace*{-3.5mm}

{\bf UAH ISEEM Departmental Scholarship}, Univ. Alabama Huntsville, 2019 (\$250)
\vspace*{-3.5mm}

{\bf IFREE Workshop Sponsorship}, International Foundation for Research in Experimental Economics, 2019 (\$250)
\vspace*{-3.5mm}

{\bf STEM Scholarship}, World Championship Punkin Chunkin Association, 2017 (\$1,750)
\vspace*{-3.5mm}

{\bf Boeing Entrepreneurship Award}, Boeing, 2016 (\$5,000)
\vspace*{-3.5mm}

{\bf UAH Presidential Scholarship}, Univ. Alabama Huntsville, 2015-2019 (full tuituion)
\vspace*{-3.5mm}

{\bf Clark Grant}, The Clark Group, 2015 (\$4,000)
\vspace*{-3.5mm}




\vspace{.75cm}
\section{\sc Programming Languages} 
{\bf Advanced}:  R (tidyverse, Shiny, custom packages), SQL, regex, git/github, Powerpoint
\vspace*{-3mm}

{\bf Proficient}:  \LaTeX, Matlab, python, Tableau, Minitab, Stata, Adobe Creative Suite
\vspace*{-3mm}

{\bf Beginner}:  SAS, C++, HTML/CSS, Simio
\vspace*{-3mm}

{\bf Misc. Skills}: Woodworking. 

\vspace{.75cm}
\section{\sc Certifications}
{\bf Six Sigma} Green Belt, ASQ, Spring 2018
\vspace*{-3mm}

{\bf Tableau} Desktop Specialist, Tableau, Fall 2019. \href{https://www.credly.com/badges/e9a605a8-1977-4a1c-ab24-149a37c7fb36/linked_in_profile}{Link}.
\vspace*{-3mm}

{\bf Engineer-in-Training} Alabama FE, NCEES, Spring 2019
\vspace*{-3mm}

{\bf Master Tutor} CLRA, Spring 2018
\vspace*{-3mm}

\vspace{.75cm}
\section{\sc Workshop Participation}
    {\bf Study Abroad}, Summer 2019, Germany and South Africa\\
    {Studied at the German DLR Aerospace Center and South African National Space Agency. Topics include space weather, plasma physics, particle transport theory, magneto-hydrodynamics, and magnetism. Projects included the mathematics of shock-waves which result from collision of the solar wind with Earth's magnetosphere, and building an antenna to receive NOAA weather satellite data and reproduce images of the earth.}
    
    {\bf Experimental Economics Workshop}, Summer 2019, Tuscaloosa, AL\\
    {Selected to participate in the International Foundation for Research in Experimental Economics, hosted by the University of Alabama.}
    
    {\bf Boeing Accelerated Student Experience}, Summer 2016, Seattle, WA\\
    {Selected to participate in the inaugural workshop for promising entrepreneurial students.}

\vspace{.75cm}
\section{\sc Research Assistance}
  \href{https://www.federalreserve.gov/econres/notes/feds-notes/research-data-series-index-of-common-inflation-expectations-20210305.htm}{Common Inflation Expectations}; Hie Joo Ahn, Federal Reserve Board. R and matlab for model specification, verification, and automation. 

\vspace{.75cm}
 \section{\sc Educational Experience}
 

    {\bf Independent Online Tutoring}, Summer 2020\\
    {Tutored various college students in Economics, Statistics, and Data Analysis courses.}

    {\bf Teaching Assistant}, Georgia Tech, Fall 2019 - Spring 2020\\
    {Assisted various professors in proctoring and grading exams. Light-weight research assistance and data collection.}
    
    {\bf Tutoring Content Development}, Univ Alabama Huntsville, Summer 2019\\
    {Created handout sheets for UAH Student Success Center for introductory statistics, thermodynamics, mechanics of materials, and calculus. Designed the curriculum from scratch and created using MS Word with PowerPoint graphics and Latex formulas.}

\vspace{.75cm}
\section{\sc Volunteer and Outreach}

{\bf Teaching Assistant}, {\it Intro to Economics \& Data Analysis}, Howard University, Fall 2019.
{Helped students 1:1 in office hours with R programming. Created tips \& tricks videos.}

{\bf Engineering Education Outreach}, Univ Alabama Huntsville.
{Developed fun and engaging STEM projects and deployed them in local middle and high schools.}


\end{resume}

\end{document}