\documentclass[margin, line]{res}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\usepackage{fontawesome5}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0.04in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0.05in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{\dimexpr 26pt-0.05in}}}
    {\end{list}}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0} 

\usepackage{array}
\newcolumntype{L}{>{\arraybackslash}p{4.5in}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\name{Michael Boerman \vspace*{2mm}}
\address{Data scientist with M.S. and 3 years experience driving decisions by modeling financial and economic data.}
\begin{resume}

\vspace{-1mm}
\section{\sc Contact}

\faEnvelope  \hspace{0.5mm} {\ttfamily michaelboerman@hey.com} \hspace{3mm}
\faPhone  \hspace{0.5mm} {\ttfamily 484-219-7563} \hspace{8.5mm}
\faLinkedinIn  \hspace{0.5mm} \href{https://www.linkedin.com/in/michael-boerman}{\ttfamily linkedin.com/in/michael-boerman}\\
\vspace{-5mm}


\section{\sc Portfolio}
\faBriefcase \hspace{0.5mm} \href{https://www.michaelboerman.com/}{\ttfamily www.michaelboerman.com} \hspace{3.5mm}
\faIcon{video} \hspace{0.5mm} \href{https://www.youtube.com/watch?v=NswRVSZcy7M}{YouTube channel} \hspace{2mm}
\faChartLine \hspace{0.5mm} \href{https://michaelboerman.shinyapps.io/covid_percentiles/}{ Covid: How Long Did You Last?}\\
\vspace{-.35cm}


\section{\sc Professional \\ Job History }

{\bf Discover Financial Services}\\

\vspace{-.65cm}
Lead Data Science Analyst \hfill October 2022 - Present\\
\hspace*{3mm} 
    Summary: Forecast credit chard charge-off rates using time series econometrics
\hspace*{3mm}
    \begin{list2}
        \item Transformed messy development time-series and machien learning code (Python, R) into fully-tested, scalable production code.
        \item Created and maintained documentation for every process owned by the team using markdown and git under the Diataxis documentation framework.
        \item Transitioned the team's file and code management from local storage to Sharepoint and Github.
    \end{list2}

{\bf Federal Reserve Board of Governors}\\

\vspace{-.65cm}

Financial Systems Analyst (Data Engineering) \hfill December 2021 - October 2022\\
\hspace*{3mm} 
    Summary: Automate data ingestion and analysis for financial regulation data (CCAR).
\hspace*{3mm}
    \begin{list2}
        \item Automated business processes, data ingestion, and data analysis with R, Python, and SQL.
        \item Communicated performance metrics by creating interactive dashboards in R Shiny and Tableau.
        \item Created machine learning models to detect outliers in bank submission data.
    \end{list2}


Senior Research Assistant (Data Science) \hfill May 2020 - December 2021 \\
\hspace*{3mm}
    Summary: Developed inflation and GDP forecasting models used in FOMC monetary policy.
\vspace{-3mm}

\hspace*{3mm}
    Links to Work:  \href{https://michaelboerman.medium.com/predicting-the-present-a56ff704af0b}{Predicting the Present} and   \href{https://github.com/michaelboerman/lockdown_severity_index#readme}{Covid Lockdown Severity Index}
    
    \begin{list2}
        \item Collaborated with economists to create statistical models and econometric forecasts using state-space time series, dynamic factor models, and ARIMA models.
        \item Deployed models to production using Gitlab CI/CD pipelines.
        \item Wrote and refactored code in R and Matlab for more than 10 statistical models and over 50 unique visualizations across 30 git repositories. 
        \item Developed and maintained 3 in-house R packages with over 100 functions used in more than 250 scripts.
        \item Built a documentation website in R Shiny for version-controlled, wiki-based documention.
    \end{list2}


\section{\sc Education }

{\bf Georgia Institute of Technology}, Atlanta, GA, USA \hfill August 2019 - May 2020\\
M.S. in Applied Economics, concentration in statistics and econometrics \hfill GPA: 4.0


{\bf University of Alabama in Huntsville}, Huntsville, AL, USA \hfill August 2015 - May 2019 \\
B.S. in Industrial \& Systems Engineering; minor in Astrophysics \hfill GPA: 4.0

\section{\sc Competencies} 
Time series analysis, econometrics, forecasting, regression analysis, predictive modeling, ETL/ELT, database development, data visualization, git version control, Agile, CI/CD, technical writing

\section{\sc Programming} 
Python, R, SQL (Postgres, Snowflake), Airflow, git, linux, shell/bash, Tableau, MATLAB

\end{resume}

\end{document}