\documentclass[margin, line]{res}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\usepackage{fontawesome5}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0.04in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0.05in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{\dimexpr 26pt-0.05in}}}
    {\end{list}}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.0} 

\usepackage{array}
\newcolumntype{L}{>{\arraybackslash}p{4.5in}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\name{Michael Boerman \vspace*{2mm}}
\address{Data scientist with M.S. and 3 years experience driving decisions by modeling financial and economic data.}
\begin{resume}

\vspace{-1mm}
\section{\sc Contact}

\faEnvelope  \hspace{1mm} {\ttfamily michaelboerman@hey.com} \hspace{7mm}
\faPhone  \hspace{1mm} {\ttfamily 484-219-7563} \hspace{10mm}
\faBriefcase \hspace{1mm} \href{https://www.michaelboerman.com/}{\ttfamily www.michaelboerman.com} \hspace{3.5mm}

\vspace{0mm}


\section{\sc Projects}

\faChartLine \hspace{0.5mm} \href{https://michaelboerman.github.io/lockdown_severity_index/}{Covid Lockdown Severity Index}
    \begin{list2}
        \item Computed national and state indices to measure Covid-era lockdown policies
        \item Previously used at the Federal Reserve Board; now free and open-source
        \item Consulted for students and universities on creating similar indices
    \end{list2}

\faIcon{video} \hspace{0.5mm} \href{https://www.youtube.com/@explainedbymichael/videos}{YouTube channel for statistics education}
    \begin{list2}
        \item 3,000+ subscribers, 250k views, 2.5m impressions, 99\% like rate
        \item 100\% free (no monetization, no sponsors)
    \end{list2}

\vspace{-.35cm}


\section{\sc Professional \\ Job History }

{\bf Discover Financial Services}\\

\vspace{-.65cm}
Lead Data Science Analyst \hfill October 2022 - Present\\
\hspace*{3mm} 
    Summary: Forecast credit chard charge-off rates using time-series econometrics.
\hspace*{3mm}
    \begin{list2}
        \item Decrease human errors and model re-runs by transforming messy development code into fully-tested, scaled, and deployed production code.
        \item Provide the CFO and VPs weekly macroeconomic summaries weekly with automated reports (SQL, Python, R).
        \item Reduce new-hire training time and increased team cross-training by writing and maintaining documentation for more than 15 processes and 7 tools using markdown and git.
        \item Transitioned the team's code management from local folders to GitHub.
    \end{list2}

{\bf Federal Reserve Board of Governors}\\

\vspace{-.65cm}

Financial Systems Analyst (Data Engineering) \hfill December 2021 - October 2022\\
\hspace*{3mm} 
    Summary: Automate data ingestion and analysis for financial regulation data (CCAR).
\hspace*{3mm}
    \begin{list2}
        \item Automated business processes, data ingestion, and data analysis (R, Python, SQL).
        \item Communicated performance metrics by creating interactive dashboards (R Shiny, Tableau).
    \end{list2}


Senior Research Assistant (Data Science) \hfill May 2020 - December 2021 \\
\hspace*{3mm}
    Summary: Developed inflation and GDP forecasting models used in FOMC monetary policy.
    
    \begin{list2}
        \item Collaborated with economists to create statistical models and forecasts using state-space time series, dynamic factor models, and ARIMA models.
        \item Deployed models to production using Gitlab CI/CD pipelines.
        \item Wrote and refactored code in R and Matlab for more than 10 statistical models and over 50 unique visualizations across 15 git repositories. 
        \item Developed and maintained 3 in-house R packages with over 100 functions used in 250+ scripts.
    \end{list2}


\section{\sc Education }

{\bf Georgia Institute of Technology}, Atlanta, GA, USA \hfill August 2019 - May 2020\\
M.S. in Applied Economics, concentration in statistics and econometrics \hfill GPA: 4.0


{\bf University of Alabama in Huntsville}, Huntsville, AL, USA \hfill August 2015 - May 2019 \\
B.S. in Industrial \& Systems Engineering; minor in Astrophysics \hfill GPA: 4.0

\end{resume}

\end{document}